---
title: "Online appendix for: Inconsistent shifts in warming and temperature variability negatively impact avian fitness."
author:
  - Conor C. Taff
  - J. Ryan Shipley
header-includes:
  - \usepackage[font={footnotesize}, labelfont={bf}]{caption}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  - \usepackage{float}
  - \floatplacement{figure}{H}
  #- \usepackage{setspace}\doublespacing
  #- \usepackage{lineno}\linenumbers
fontsize: 12pt
output: 
  bookdown::html_document2:
      number_sections: FALSE
      toc: TRUE
bibliography: references.bib
csl: nature-communications.csl
---

This document includes full model tables and summaries to accompany Taff & Shipley. Please see the paper for descriptions of output.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, APCtools, itsadug, here)

num_fled_inc <- readRDS(here::here("2_modified_data", "num_fled_inc.rds"))
num_fled_nest <- readRDS(here::here("2_modified_data", "num_fled_nest.rds"))
```



```{r gam-table, echo = FALSE, message = FALSE, warning = FALSE}

# function to format gam tables for the individual species models
      gam_tab_fxn <- function(model1, model2){
        tab_out <- as.data.frame(matrix(nrow = 12, ncol = 10))
        colnames(tab_out) <- c("Label", "Term", "Est", "SE", "Stat", "P", "Est2", "SE2", "Stat2", "P2")
        tab_out[1, ] <- c(NA, NA, NA, "Incubation", NA, NA, NA, "Provisioning", NA, NA)
        tab_out[2, ] <- c(NA, NA, "estimate", "std. error", "t-value", "p-value", "estimate", "std. error", "t-value", "p-value")
        tab_out[4, ] <- c(NA, NA, "edf", "ref.df", "f-value", "p-value", "edf", "ref.df", "f-value", "p-value")
        tab_out[, 1] <- c(NA, "A. Parametric coefficients", NA, "B. Smooth terms", NA, NA, NA, NA, NA, "Adjusted r-squared", "Deviance explained", "n")
        tab_out[, 2] <- c(NA, NA, "intercept", NA, "s(coldest 3-days)", "s(hottest 3-days)", "s(day of year)", "s(year)", "s(longitude, latitude)", NA, NA, NA)
        
        s1 <- summary(model1)
        s2 <- summary(model2)
        
        tab_out[3, 3:6] <- finalfit::round_tidy(s1$p.table, 3)
        tab_out[3, 7:10] <- finalfit::round_tidy(s2$p.table, 3)
        tab_out[5:9, 3:6] <- finalfit::round_tidy(s1$s.table, 3)
        tab_out[5:9, 7:10] <- finalfit::round_tidy(s2$s.table, 3)
        tab_out[10, 3] <- finalfit::round_tidy(s1$r.sq, 3)
        tab_out[10, 7] <- finalfit::round_tidy(s2$r.sq, 3)
        tab_out[11, 3] <- finalfit::round_tidy(s1$dev.expl, 3)
        tab_out[11, 7] <- finalfit::round_tidy(s2$dev.expl, 3)
        tab_out[12, 3] <- s1$n
        tab_out[12, 7] <- s2$n
        
        tab_out
  
      }

## function for the time series models
    gam_tab_fxn_time <- function(model1){
        tab_out <- as.data.frame(matrix(nrow = 8, ncol = 6))
        colnames(tab_out) <- c("Label", "Term", "Est", "SE", "Stat", "P")
        tab_out[1, ] <- c(NA, NA, "estimate", "std. error", "t-value", "p-value")
        tab_out[3, ] <- c(NA, NA, "edf", "ref.df", "f-value", "p-value")
        tab_out[, 1] <- c("A. Parametric coefficients", NA, "B. Smooth terms", NA, NA, "Adjusted r-squared", "Deviance explained", "n")
        tab_out[, 2] <- c(NA, "intercept", NA, "s(longitude, latitude)", "s(year)", NA, NA, NA)
        
        s1 <- summary(model1)
        
        tab_out[2, 3:6] <- finalfit::round_tidy(s1$p.table, 3)
        tab_out[4:5, 3:6] <- finalfit::round_tidy(s1$s.table, 3)
        tab_out[6, 3] <- finalfit::round_tidy(s1$r.sq, 3)
        tab_out[7, 3] <- finalfit::round_tidy(s1$dev.expl, 3)
        tab_out[8, 3] <- s1$n
 
        
        tab_out
    }
    
## function for the grid
    gam_tab_fxn_grid <- function(model1){
        tab_out <- as.data.frame(matrix(nrow = 9, ncol = 6))
        colnames(tab_out) <- c("Label", "Term", "Est", "SE", "Stat", "P")
        tab_out[1, ] <- c(NA, NA, "estimate", "std. error", "t-value", "p-value")
        tab_out[3, ] <- c(NA, NA, "edf", "ref.df", "f-value", "p-value")
        tab_out[, 1] <- c("A. Parametric coefficients", NA, "B. Smooth terms", NA, NA, NA, "Adjusted r-squared", "Deviance explained", "n")
        tab_out[, 2] <- c(NA, "intercept", NA, "s(spring anomaly)", "s(longitude, latitude)", "s(year)", NA, NA, NA)
        
        s1 <- summary(model1)
        
        tab_out[2, 3:6] <- finalfit::round_tidy(s1$p.table, 3)
        tab_out[4:6, 3:6] <- finalfit::round_tidy(s1$s.table, 3)
        tab_out[7, 3] <- finalfit::round_tidy(s1$r.sq, 3)
        tab_out[8, 3] <- finalfit::round_tidy(s1$dev.expl, 3)
        tab_out[9, 3] <- s1$n
 
        
        tab_out
        }
```



# Climate models

Several GAMs were fit to explore changes in average temperature anomaly and the timing of cold-snaps and heat-waves. See manuscript for descriptions of models.

## Time series for spring temperature anomaly

```{r time-avg, echo = FALSE, message = FALSE, warning = FALSE}
time_series_mods <- readRDS(here::here("6_saved_data_objects", "time_series_mods.rds"))

time_tab <- gam_tab_fxn_time(time_series_mods[[1]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of spring temperature anomly for each grid cell.")

```


## Time series for cold-snap anomaly

```{r cold-avg, echo = FALSE, message = FALSE, warning = FALSE}
## object loaded in earlier chunk

time_tab <- gam_tab_fxn_time(time_series_mods[[2]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of first cold-snap timing with a temperature threshold of 18.5C for each grid cell.")

```

```{r cold-avg16, echo = FALSE, message = FALSE, warning = FALSE}
time_tab <- gam_tab_fxn_time(time_series_mods[[3]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of first cold-snap timing with a temperature threshold of 16C for each grid cell.")

```

```{r cold-avg13, echo = FALSE, message = FALSE, warning = FALSE}
time_tab <- gam_tab_fxn_time(time_series_mods[[4]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of first cold-snap timing with a temperature threshold of 13C for each grid cell.")
```


## Time series for heat-wave anomaly


```{r hot-avg, echo = FALSE, message = FALSE, warning = FALSE}
## object loaded in earlier chunk

time_tab <- gam_tab_fxn_time(time_series_mods[[5]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of last heat-wave timing with a temperature threshold of 26C for each grid cell.")

```

```{r hot-avg31, echo = FALSE, message = FALSE, warning = FALSE}
time_tab <- gam_tab_fxn_time(time_series_mods[[6]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of last heat-wave timing with a temperature threshold of 31C for each grid cell.")

```

```{r hot-avg36, echo = FALSE, message = FALSE, warning = FALSE}
time_tab <- gam_tab_fxn_time(time_series_mods[[7]])
options(knitr.kable.NA = '')
knitr::kable(time_tab, col.names = NULL, caption = "Results of the GAM for time series of last heat-wave timing with a temperature threshold of 36C for each grid cell.")
```

## Average temperature anomaly compared to cold-snap anomaly

```{r anom-snap, echo = FALSE, message = FALSE, warning = FALSE}
m_sn95 <- readRDS(here::here("6_saved_data_objects", "m_sn95.rds"))

avg_tab <- gam_tab_fxn_time(m_sn95)
avg_tab[4, 2] <- "s(average anomaly)"
avg_tab[5, 2] <- "s(longitude, latitude)"
options(knitr.kable.NA = '')
knitr::kable(avg_tab, col.names = NULL, caption = "Average temperature anomaly compared to average cold-snap anomaly for each grid cell. Averages include years from 1995-2020.")

```

## Average Temperature anomaly compared to heat-wave anomaly

```{r anom-wave, echo = FALSE, message = FALSE, warning = FALSE}

m_hw95 <- readRDS(here::here("6_saved_data_objects", "m_hw95.rds"))

avg_tab <- gam_tab_fxn_time(m_hw95)
avg_tab[4, 2] <- "s(average anomaly)"
avg_tab[5, 2] <- "s(longitude, latitude)"
options(knitr.kable.NA = '')
knitr::kable(avg_tab, col.names = NULL, caption = "Average temperature anomaly compared to average heat-wave anomaly for each grid cell. Averages include years from 1995-2020.")

```

## Grid temperature compared to cold-snap

```{r grid-cold, echo = FALSE, message = FALSE, warning = FALSE}
cold_anom <- readRDS(here::here("6_saved_data_objects", "snap_anom.rds"))

grid_tab <- gam_tab_fxn_grid(cold_anom)
options(knitr.kable.NA = '')
knitr::kable(grid_tab, col.names = NULL, caption = "Spring temperature anomaly compared to timing of last cold-snap for each grid and year combination.")

```

## Grid temperature compared to heat-wave

```{r grid-hot, echo = FALSE, message = FALSE, warning = FALSE}
heat_anom <- readRDS(here::here("6_saved_data_objects", "heat_anom.rds"))
grid_tab <- gam_tab_fxn_grid(heat_anom)
options(knitr.kable.NA = '')
knitr::kable(grid_tab, col.names = NULL, caption = "Spring temperature anomaly compared to timing of last heat-wave for each grid and year combination.")

```

# Species susceptibility to temperature extremes

One model was fit for each of 24 species using incubation measures and a second model was fit using provisioning measures. The two models for each species are combined into one table per species. Plots are included showing the relationship between relative fitness, coldest three day period, and hottest three day period for each species during incubation and provisioning.


## Northern cardinal

```{r noca-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[1]], num_fled_nest[[1]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for northern cardinal breeding records during incubation and provisioning.")
```

```{r noca-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for northern cardinal breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[1]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[1]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## House finch

```{r hofi-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[2]], num_fled_nest[[2]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for house finch breeding records during incubation and provisioning.")
```

```{r hofi-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for house finch breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[2]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[2]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Barn swallow

```{r bars-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[3]], num_fled_nest[[3]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for barn swallow breeding records during incubation and provisioning.")
```

```{r bars-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for barn swallow breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[3]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[3]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Black-capped chickadee

```{r bcch-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[4]], num_fled_nest[[4]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for black-capped chickadee breeding records during incubation and provisioning.")
```

```{r bcch-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for black-capped chickadee breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[4]], plot.type = "contour", too.far = 0.05, xlim = c(-3.5, 3.5), ylim = c(-3.5, 3.5),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[4]], plot.type = "contour", too.far = 0.05, xlim = c(-3.5, 3.5), ylim = c(-3.5, 3.5),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Purple martin

```{r puma-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[5]], num_fled_nest[[5]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for purple martin breeding records during incubation and provisioning.")
```

```{r puma-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for purple martin breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[5]], plot.type = "contour", too.far = 0.05, xlim = c(-5.5, 4.5), ylim = c(-5.5, 4.5),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-5, 4, "A")

vis.gam(num_fled_nest[[5]], plot.type = "contour", too.far = 0.05, xlim = c(-5.5, 4.5), ylim = c(-5.5, 4.5),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-5, 4, "B")

```

## Eastern phoebe

```{r eaph-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[6]], num_fled_nest[[6]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for eastern phoebe breeding records during incubation and provisioning.")
```

```{r eaph-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for eastern phoebe breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[6]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[6]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Eastern bluebird

```{r eabl-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[7]], num_fled_nest[[7]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for eastern bluebird breeding records during incubation and provisioning.")
```

```{r eabl-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for eastern bluebird breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[7]], plot.type = "contour", too.far = 0.05, xlim = c(-4.5, 3.5), ylim = c(-4.5, 3.5),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-4, 3, "A")

vis.gam(num_fled_nest[[7]], plot.type = "contour", too.far = 0.05, xlim = c(-4.5, 3.5), ylim = c(-4.5, 3.5),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-4, 3, "B")

```

## Tree swallow

```{r tres-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[8]], num_fled_nest[[8]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for tree swallow breeding records during incubation and provisioning.")
```

```{r tres-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for tree swallow breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[8]], plot.type = "contour", too.far = 0.05, xlim = c(-4, 4), ylim = c(-4, 4),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-3.5, 3.5, "A")

vis.gam(num_fled_nest[[8]], plot.type = "contour", too.far = 0.05, xlim = c(-4, 4), ylim = c(-4, 4),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-3.5, 3.5, "B")

```

## House wren

```{r howr-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[9]], num_fled_nest[[9]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for house wren breeding records during incubation and provisioning.")
```

```{r howr-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for house wren breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[9]], plot.type = "contour", too.far = 0.05, xlim = c(-4.5, 4), ylim = c(-4.5, 4),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-4, 3.5, "A")

vis.gam(num_fled_nest[[9]], plot.type = "contour", too.far = 0.05, xlim = c(-4.5, 4), ylim = c(-4.5, 4),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-4, 3.5, "B")

```

## American robin

```{r amro-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[10]], num_fled_nest[[10]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for American robin breeding records during incubation and provisioning.")
```

```{r amro-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for American robin breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[10]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[10]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Mourning dove

```{r modo-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[11]], num_fled_nest[[11]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for mourning dove breeding records during incubation and provisioning.")
```

```{r modo-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for mourning dove breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[11]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[11]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## White-breasted nuthatch

```{r wbnu-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[12]], num_fled_nest[[12]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for white-breasted nuthatch breeding records during incubation and provisioning.")
```

```{r wbnu-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for white-breasted nuthatch breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[12]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[12]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Prothonotary warbler

```{r prow-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[13]], num_fled_nest[[13]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for prothonotary warbler breeding records during incubation and provisioning.")
```

```{r prow-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for prothonotary warbler breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[13]], plot.type = "contour", too.far = 0.05, xlim = c(-4, 4), ylim = c(-3, 4),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[13]], plot.type = "contour", too.far = 0.05, xlim = c(-4, 4), ylim = c(-4, 4),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Tufted titmouse

```{r tuti-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[14]], num_fled_nest[[14]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for tufted titmouse breeding records during incubation and provisioning.")
```

```{r tuti-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for tufted titmouse breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[14]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[14]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Carolina chickadee

```{r cach-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[15]], num_fled_nest[[15]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for carolina chickadee breeding records during incubation and provisioning.")
```

```{r cach-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for carolina chickadee breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[15]], plot.type = "contour", too.far = 0.05, xlim = c(-4, 3), ylim = c(-4, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[15]], plot.type = "contour", too.far = 0.05, xlim = c(-4, 3), ylim = c(-4, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Mountain chickadee

```{r moch-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[16]], num_fled_nest[[16]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for mountain chickadee breeding records during incubation and provisioning.")
```

```{r moch-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for mountain chickadee breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[16]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[16]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Chestnut-backed chickadee

```{r cbch-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[17]], num_fled_nest[[17]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for chestnut-backed chickadee breeding records during incubation and provisioning.")
```

```{r cbch-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for chestnut-backed chickadee breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[17]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[17]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Mountain bluebird

```{r mobl-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[18]], num_fled_nest[[18]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for mountain bluebird breeding records during incubation and provisioning.")
```

```{r mobl-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for mountain bluebird breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[18]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[18]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Western bluebird

```{r webl-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[19]], num_fled_nest[[19]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for western bluebird breeding records during incubation and provisioning.")
```

```{r webl-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for western bluebird breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[19]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[19]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Violet green swallow

```{r vgsw-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[20]], num_fled_nest[[20]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for violet green swallow breeding records during incubation and provisioning.")
```

```{r vgsw-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for violet green swallow breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[20]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[20]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Bewick's wren

```{r bewr-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[21]], num_fled_nest[[21]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for bewick's wren breeding records during incubation and provisioning.")
```

```{r bewr-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for bewick's wren breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[21]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[21]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Oak titmouse

```{r oati-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[22]], num_fled_nest[[22]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for oak tit breeding records during incubation and provisioning.")
```

```{r oati-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for oak titmouse breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[22]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[22]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Brown-headed nuthatch

```{r bhnu-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[23]], num_fled_nest[[23]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for brown-headed nuthatch breeding records during incubation and provisioning.")
```

```{r bhnu-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for brown-headed nuthatch breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[23]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[23]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

## Black crested titmouse

```{r bcti-tab, echo = FALSE, message = FALSE, warning = FALSE}
taber <- gam_tab_fxn(num_fled_inc[[24]], num_fled_nest[[24]])
options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAMs for black-crested titmouse breeding records during incubation and provisioning.")
```

```{r bcti-fig, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 4.5, fig.width = 8.3, fig.cap = "Contour plots from GAM fits for black crested titmouse breeding during (A) incubation and (B) provisioning. Contour lines and colors indicate relative fitness where average fitness across all records included in the model equals one. White areas of the plot did not have any observed data."}

par(mfrow = c(1, 2))
vis.gam(num_fled_inc[[24]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "A")

vis.gam(num_fled_nest[[24]], plot.type = "contour", too.far = 0.05, xlim = c(-3, 3), ylim = c(-3, 3),
        xlab = "Coldest 3-day period (sd units)", ylab = "Hottest 3-day period (sd units)", main = "")
text(-2.6, 2.6, "B")

```

# Latitudinal variation in susceptibility

## Eastern bluebird

```{r eabl-lat1, echo = FALSE, message = FALSE, warning = FALSE}
eabl_incmods <- readRDS(here::here("6_saved_data_objects", "eabl_incmods.rds"))
eabl_nesmods <- readRDS(here::here("6_saved_data_objects", "eabl_nesmods.rds"))

taber <- gam_tab_fxn(eabl_incmods[[1]], eabl_nesmods[[1]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for first quintile of eastern bluebird records (southernmost).")

```

```{r eabl-lat2, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(eabl_incmods[[2]], eabl_nesmods[[2]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for second quintile of eastern bluebird records (20th-40th percentile southern).")

```

```{r eabl-lat3, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(eabl_incmods[[3]], eabl_nesmods[[3]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for middle quintile of eastern bluebird records.")

```

```{r eabl-lat4, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(eabl_incmods[[4]], eabl_nesmods[[4]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for fourth quintile of eastern bluebird records (60th-80th percentile northern).")

```

```{r eabl-lat5, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(eabl_incmods[[5]], eabl_nesmods[[5]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for fifth quintile of eastern bluebird records (northernmost).")

```



## Purple martin

```{r puma-lat, echo = FALSE, message = FALSE, warning = FALSE}
puma_incmods <- readRDS(here::here("6_saved_data_objects", "puma_incmods.rds"))
puma_nesmods <- readRDS(here::here("6_saved_data_objects", "puma_nesmods.rds"))

```

```{r puma-lat1, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(puma_incmods[[1]], puma_nesmods[[1]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for first quintile of purple martin records (southernmost).")

```

```{r puma-lat2, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(puma_incmods[[2]], puma_nesmods[[2]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for second quintile of purple martin records (20th-40th percentile southern).")

```

```{r puma-lat3, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(puma_incmods[[3]], puma_nesmods[[3]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for middle quintile of purple martin records.")

```

```{r puma-lat4, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(puma_incmods[[4]], puma_nesmods[[4]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for fourth quintile of purple martin records (60th-80th percentile northern).")

```

```{r puma-lat5, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(puma_incmods[[5]], puma_nesmods[[5]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for fifth quintile of purple martin records (northernmost).")

```


## Tree swallow

```{r tres-lat, echo = FALSE, message = FALSE, warning = FALSE}
tres_incmods <- readRDS(here::here("6_saved_data_objects", "tres_incmods.rds"))
tres_nesmods <- readRDS(here::here("6_saved_data_objects", "tres_nesmods.rds"))

```

```{r tres-lat1, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(tres_incmods[[1]], tres_nesmods[[1]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for first quintile of tree swallow records (southernmost).")

```

```{r tres-lat2, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(tres_incmods[[2]], tres_nesmods[[2]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for second quintile of tree swallow records (20th-40th percentile southern).")

```

```{r tres-lat3, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(tres_incmods[[3]], tres_nesmods[[3]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for middle quintile of tree swallow records.")

```

```{r tres-lat4, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(tres_incmods[[4]], tres_nesmods[[4]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for fourth quintile of tree swallow records (60th-80th percentile northern).")

```

```{r tres-lat5, echo = FALSE, message = FALSE, warning = FALSE}

taber <- gam_tab_fxn(tres_incmods[[5]], tres_nesmods[[5]])

options(knitr.kable.NA = '')
knitr::kable(taber, col.names = NULL, caption = "Results of GAM for fifth quintile of tree swallow records (northernmost).")

```

